A Catalogue of Twists of Supersymmetric Gauge Theories

### 2020-01-17 paper.tex
N=1 table

We first decompose the fields of the 4-dimensional $\mc N=1$ theory with respect to the ${\rm U}(2)$ stabilizer.
The fields of the pure Yang-Mills part decomposes as:
\begin{align*}
c & \mapsto A_{0} \in \Omega^0(\CC^2 ; \fg) \\
A & \mapsto A_{0,1} + A_{1,0} \in \Omega^{0,1}(\CC^2 ; \fg) \oplus \Omega^{1,0}(\CC^2 ; \fg) \\
\lambda_- & \mapsto \lambda_{1,0} \in \Omega^{1,0}(\CC^2 ; \fg) \\
\lambda_+ & \mapsto \lambda_0 + A_{0,2} \in \Omega^{0}(\CC^2 ; \fg) \oplus \Omega^{0,2}(\CC^2 ; \fg) \\
\phi & \mapsto \phi \in \Omega^0 (\CC^2 ; R^*) \\
\Bar{\phi} & \mapsto \gamma_0 \in \Omega^{2,2}(\CC^2 ; R) \\
\psi_+ & \mapsto \psi_0 + \beta_{2,0} \in \Omega^{0}(\CC^2 ; R^*) \oplus \Omega^{2,0}(\CC^2 ; R^*) \\
\psi_- & \mapsto \gamma_{0,1} \in \Omega^{0,1}(\CC^2 ; R)
\end{align*}
and their antifields:
\begin{align*}
c^* & \mapsto B_{2,2} \in \Omega^{2,2}(\CC^2 ; \fg) \\
A^* & \mapsto B_{2,1} + A^*_{1,0} \in \Omega^{2,1}(\CC^2;\fg) \oplus \Omega^{1,2}(\CC^2; \fg) \\
\lambda^*_- & \mapsto \lambda_{1,0}^* \in \Omega^{1,2}(\CC^2 ; \fg) \\
\lambda^*_+ & \mapsto \lambda_0^*+ B_{2,0} \in \Omega^{0}(\CC^2 ; \fg) \oplus \Omega^{2,0}(\CC^2 ; \fg) \\
\phi^* & \mapsto \phi^* \in \Omega^{2,2}(\CC^2 ; R^*) \\
\Bar{\phi}^* & \mapsto \beta_{2,2} \in \Omega^{2,2} (\CC^2 ; R) \\
\psi^*_+ & \mapsto \psi_{2,2}^* + \gamma_{0,2} \in \Omega^{2,2}(\CC^2 ; R) \oplus \Omega^{0,2}(\CC^2 ; R) \\
\psi^*_- & \mapsto \beta_{2,1} \in \Omega^{2,1}(\CC^2 ; R)
\end{align*}

@@

\begin{align*}
S_{\mr{gauge}} &= \int \dvol \left(-(F^{2, 0}, F^{0, 2}) - \frac{1}{4}(\Lambda F_{1, 1})^2\right) + \frac 12 \left(\lambda_{1,0} \wedge \dd_{A_{1,0}} A_{0,2}) + \omega (\lambda_{1,0} \wedge \dbar_{A_{0,1}} \lambda_0) \right)  \\
S_{\mr{matter}} &= \int \bigg( \dvol ((\dd_{A_{1,0}}\phi , \ol \dd_{A_{0,1}} \gamma_0) + (\dd_{A_{1,0}}\gamma_0, \ol \dd_{A_{0,1}} \phi)) + \omega (\psi_0 \partial_{A_{1,0}} \gamma_{0,1}) + \beta_{2,0} \dbar_{A_{0,1}} \gamma_{0,1}  + \\
&\qquad + 2\dvol(([\lambda_0,\nu],\nu') + ([\chi, \psi_0], \nu') )   \bigg) \\
S_{\mr{anti}} &= \int \dd_{A_{1, 0}} A_0 \wedge A_{1,0}^* + \ol\dd_{A_{0, 1}} A_0\wedge B_{2,1} + [\lambda_{1,0}, A_0]\wedge \lambda_{1,0}^* +  [\lambda_{0}, A_0]\wedge \lambda_{0}^* +B_{2,1} \wedge [A_0, A_{0,1}] + A_{1,0}^* \wedge [A_{0}, A_{1,0}] \\
&\qquad + \frac{1}{2}[A_0, A_0]A_0^* + [\phi, A_0] \phi^* + [\gamma_0, A_0] \beta_{2,2} + [\gamma_{0,1}, A_0]\wedge \beta_{2,1} + [\psi_0, A_0] \psi_0^* + [\beta_{2,0}, A_0] \wedge \gamma_{0,2} \\
I^{(1)}_{\mr{gauge}} &=  \int \dvol \left( - (\lambda_{1,0}, A_{0,1}^*) + \frac 12 (F_{0,2},B_{2,0}) + \frac 12 (F_{1,1}, \lambda_0^*)  \right)\\
I^{(1)}_{\mr{matter}} &=  \int \dvol \left( (\phi, \psi_0^*) + \frac 12( \ol \dd_{A_{0,1}} \gamma_{0}, \beta_{2,1}) \right)\\
I^{(2)}_{\mr{gauge}} &= -\frac{1}{4}\int \dvol (\lambda_0^*)^2.
\end{align*}
Here, in terms of the K\"ahler form $\omega$, the volume form is identified as $\dvol = \frac{\omega^2}2$.

>>>>

We first decompose the fields of the 4-dimensional $\mc N=1$ theory with respect to the ${\rm U}(2)$ stabilizer.
The fields of the pure Yang-Mills part decomposes as:
\[
\begin{array} {lllcccccc}
& &  & {\rm Untwisted} & R & {\rm Twisted}  \\
c & \mapsto & A_{0} \in \Omega^0(\CC^2 ; \fg) & -1 & 0 & -1 \\
A & \mapsto & A_{0,1} + A_{1,0} \in \Omega^{0,1}(\CC^2 ; \fg) \oplus \Omega^{1,0}(\CC^2 ; \fg) & 0 & 0 & 0 \\
\lambda_- & \mapsto & \lambda_{1,0} \in \Omega^{1,0}(\CC^2 ; \fg) & 0 & -1 & -1 \\
\lambda_+ & \mapsto & \lambda_0 + A_{0,2} \in \Omega^{0}(\CC^2 ; \fg) \oplus \Omega^{0,2}(\CC^2 ; \fg) & 0 & +1 & + 1 \\
\phi & \mapsto & \phi \in \Omega^0 (\CC^2 ; R^*) & 0 & 0 & 0 \\
\Bar{\phi} & \mapsto & \gamma_0 \in \Omega^{0,0}(\CC^2 ; R) & 0 & 0 & 0 \\
\psi_+ & \mapsto & \psi_0 + \beta_{2,0} \in \Omega^{0}(\CC^2 ; R^*) \oplus \Omega^{2,0}(\CC^2 ; R^*) & 0 & -1 & -1 \\
\psi_- & \mapsto & \gamma_{0,1} \in \Omega^{0,1}(\CC^2 ; R) & 0 & +1 & +1 
\end{array}
\]
\brian{Is it necessary to put in the antifields?} 
and their antifields:
\begin{align*}
c^* & \mapsto B_{2,2} \in \Omega^{2,2}(\CC^2 ; \fg) \\
A^* & \mapsto B_{2,1} + A^*_{1,0} \in \Omega^{2,1}(\CC^2;\fg) \oplus \Omega^{1,2}(\CC^2; \fg) \\
\lambda^*_- & \mapsto \lambda_{1,0}^* \in \Omega^{1,2}(\CC^2 ; \fg) \\
\lambda^*_+ & \mapsto \lambda_0^*+ B_{2,0} \in \Omega^{0}(\CC^2 ; \fg) \oplus \Omega^{2,0}(\CC^2 ; \fg) \\
\phi^* & \mapsto \phi^* \in \Omega^{2,2}(\CC^2 ; R^*) \\
\Bar{\phi}^* & \mapsto \beta_{2,2} \in \Omega^{2,2} (\CC^2 ; R) \\
\psi^*_+ & \mapsto \psi_{2,2}^* + \gamma_{0,2} \in \Omega^{2,2}(\CC^2 ; R) \oplus \Omega^{0,2}(\CC^2 ; R) \\
\psi^*_- & \mapsto \beta_{2,1} \in \Omega^{2,1}(\CC^2 ; R)
\end{align*}

@@

\begin{align*}
S_{\mr{gauge}} &= \int \left(-(F^{2, 0}, F^{0, 2}) - \frac{1}{4}(\Lambda F_{1, 1})^2\right) + \frac 12 \left(\lambda_{1,0} \wedge \dd_{A_{1,0}} A_{0,2}) + \omega (\lambda_{1,0} \wedge \dbar_{A_{0,1}} \lambda_0) \right)  \\
S_{\mr{matter}} &= \int \bigg( ((\dd_{A_{1,0}}\phi , \ol \dd_{A_{0,1}} \gamma_0) + (\dd_{A_{1,0}}\gamma_0, \ol \dd_{A_{0,1}} \phi)) + \omega (\psi_0 \partial_{A_{1,0}} \gamma_{0,1}) + \beta_{2,0} \dbar_{A_{0,1}} \gamma_{0,1}  + \\
&\qquad + 2 (([\lambda_0,\nu],\nu') + ([\chi, \psi_0], \nu') )   \bigg) \\
S_{\mr{anti}} &= \int \dd_{A_{1, 0}} A_0 \wedge A_{1,0}^* + \ol\dd_{A_{0, 1}} A_0\wedge B_{2,1} + [\lambda_{1,0}, A_0]\wedge \lambda_{1,0}^* +  [\lambda_{0}, A_0]\wedge \lambda_{0}^* +B_{2,1} \wedge [A_0, A_{0,1}] + A_{1,0}^* \wedge [A_{0}, A_{1,0}] \\
&\qquad + \frac{1}{2}[A_0, A_0]A_0^* + [\phi, A_0] \phi^* + [\gamma_0, A_0] \beta_{2,2} + [\gamma_{0,1}, A_0]\wedge \beta_{2,1} + [\psi_0, A_0] \psi_0^* + [\beta_{2,0}, A_0] \wedge \gamma_{0,2} \\
I^{(1)}_{\mr{gauge}} &=  \int  \left( - (\lambda_{1,0}, A_{0,1}^*) + \frac 12 (F_{0,2},B_{2,0}) + \frac 12 (F_{1,1}, \lambda_0^*)  \right)\\
I^{(1)}_{\mr{matter}} &=  \int  \left( (\phi, \psi_0^*) + \frac 12( \ol \dd_{A_{0,1}} \gamma_{0}, \beta_{2,1}) \right)\\
I^{(2)}_{\mr{gauge}} &= -\frac{1}{4}\int  (\lambda_0^*)^2.
\end{align*}
Here, in terms of the K\"ahler form $\omega$, the volume form is identified as $\dvol = \frac{\omega^2}2$.
